\documentclass[11pt]{article}

\usepackage{a4wide}
\usepackage{mathptm}
\usepackage{xspace}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{tikz}
\usepackage{tkz-graph}
\usetikzlibrary{shapes.misc, positioning}
\usepackage{listings}
\usepackage{color}
\usepackage{hyperref}
\usepackage{setspace} 
\usepackage{microtype}
\usepackage{tocloft}
\usepackage{titlesec}
\usepackage{abstract} 
\usepackage{subcaption}
\usepackage{float}  
    
\setlength{\absleftindent}{0pt}       
\setlength{\absrightindent}{0pt}

\setlength{\parindent}{0pt}
\setlength{\parskip}{0.6em}
\setcounter{tocdepth}{3}
\titleformat{\section}{\LARGE\bfseries}{\thesection}{0.5em}{}    
\titleformat{\subsection}{\Large\bfseries}{\thesubsection}{0.5em}{}
\titleformat{\subsubsection}{\normalsize\bfseries}{\thesubsubsection}{0.5em}{}

\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{mauve}{rgb}{0.58,0,0.82}

\lstset{frame=tb,
  language=Java,
  aboveskip=3mm,
  belowskip=3mm,
  showstringspaces=false,
  columns=flexible,
  basicstyle={\small\ttfamily},
  numbers=left,
  numberstyle=\tiny\color{gray},
  keywordstyle=\color{blue},
  commentstyle=\color{dkgreen},
  stringstyle=\color{mauve},
  breaklines=true,
  breakatwhitespace=true,
  tabsize=3
}
\lstdefinelanguage{JavaScript}{
  keywords={typeof, new, true, false, function, return, null, switch, var, let, const,
    if, in, while, for, break, do, case, else, import, export, from, as, class, extends,
    super, try, catch, finally, throw, async, await, yield},
  sensitive=true,
  comment=[l]{//},
  morecomment=[s]{/*}{*/},
  morestring=[b]',
  morestring=[b]"
}
\lstdefinelanguage{TypeScript}[]{JavaScript}{
  morekeywords={interface,type,implements,readonly,public,private,protected,enum,unknown,keyof,asserts,satisfies}
}
\lstdefinelanguage{yaml}{
  sensitive=true,
  comment=[l]{\#},
  morestring=[b]',
  morestring=[b]",
}

\begin{document}

\title{DAT250 FeedApp Report}

\author{Erlend André Høntorp, Jonas Heen Opsahl and Thomas Tolo Jensen}
\onehalfspacing

\maketitle

\begin{abstract}
Live polling applications need to keep data consistent across many users 
while staying fast and responsive. FeedApp is a real-time polling platform 
where users can create polls, vote, and discuss results in comment threads, 
with updates appearing instantly for everyone. This report compares RabbitMQ 
(message queuing) and Kafka (
event sourcing) for handling real-time updates in a web application. Our aim 
is to show how a queue-oriented broker differs from a log-centric event stream 
in throughput, latency, scaling, and fan-out. We built the system with a Spring Boot backend 
and React frontend, using Kafka's topic-per-poll approach along with Redis 
for caching and WebSockets for push notifications. We used the OpenMessaging
Benchmark to test both systems under different loads that simulate many votes 
coming in and updates being pushed to users. In our tests, Kafka handled more 
messages per second and scaled better when there were lots of writes, and 
RabbitMQ did not have lower latency at low message rates in our setup. As the 
load increased, Kafka pulled ahead, and RabbitMQ’s per‑message overhead became 
a bottleneck. Using one Kafka topic per
poll kept events clean and isolated, but it added some extra management work. 
Overall, we learned about the trade‑off between throughput and latency in 
log‑based (Kafka) vs queue‑based (RabbitMQ) systems, when the extra complexity 
of an event‑driven design makes sense, and why careful cache invalidation matters 
in a distributed app.
\end{abstract}

\clearpage
\tableofcontents
\clearpage

%\input{commands}

\input{sections/introduction}

\input{sections/design}

\input{sections/technology}

\input{sections/implementation}

\input{sections/conclusion}

\bibliographystyle{plain}
\bibliography{report.bib}{}

\end{document}
